Multi-level modelling with Openflexo/FML - A contribution to the \mpc

### 2021-05-28 5-Analysis.tex
synchro from overleaf
replace ie by macro

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). As the figure shows the VirtualModels play the role of metamodels, in the sens of concept definition with a level-blind approach. The VirtualModel instances play the role of models conform to metamodel definitions. In the rest of the paper, we keep the the vocabulary metamodels and models as to simplify the presentation.
The resulted architecture follows the way the challenge is presented and this organisation allows for the possibility of flexible extensions.

@@

\item the vertical axis is viewed as the linguistic instantiation, relative to the use of the FML language. The VirtualModel, defined as the core definition metamodel, generates a model founded on the instantiation mechanism of the FML Language. This mechanism is the classical Object/Instance mechanism of the object languages but without any constraint on the referenced VirtualModel, i.e metamodel. The set of resulted instances comes from several VirtualModels 
from any abstraction level as detailed in section \ref{sec:AcmeSoftwareDevelopmentProcess}

>>>>

Like any modeling approaches, these different steps could also be achieved in any order and iteratively. But our goal during the challenge's analysis remains to produce a FML VirtualModels architecture as a federation of VirtualModels. 
As shown in figure~\ref{fig:MultilevelArchitecture}, we defined two VirtualModels (Base and ACME processes abstractions) instantiatied by two VirtualModel instances (XSure and ACME processes). As the figure shows the VirtualModels play the role of metamodels, in the sense of concept definition with a level-blind approach. The VirtualModel instances play the role of models conform to metamodel definitions. In the rest of the paper, we keep the the vocabulary metamodels and models as to simplify the presentation.
The resulted architecture follows the way the challenge is presented and this organisation allows for the possibility of flexible extensions.

@@

\item the vertical axis is viewed as the linguistic instantiation, relative to the use of the FML language. The VirtualModel, defined as the core definition metamodel, generates a model founded on the instantiation mechanism of the FML Language. This mechanism is the classical Object/Instance mechanism of the object languages but without any constraint on the referenced VirtualModel, \ie metamodel. The set of resulted instances comes from several VirtualModels 
from any abstraction level as detailed in section \ref{sec:AcmeSoftwareDevelopmentProcess}
